Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-08-07 analysis/paper/paper.Rmd
update discussion

@@

Whether standardization reflects an emergence of specialized production is associated with the number of producers, which distinguishes mechanical standardization from intentional standardization [@Costin2001; @Costin1995]. In other words, mechanical standardization depends on potter's skills and experiences that increased uniformity normally reflects fewer producers.

>>>>

```{r poisson-linear-model}
total_potsherds <- read.csv(here("analysis", "data", "raw_data", "Kwl_total_potsherds.csv"))

# poisson model
fit <- glm(formula = sum_pot ~ cv_pc1,
            family = "poisson",
            data = total_potsherds)

pval <- unname(coef(summary(fit))[,'Pr(>|z|)'][2])
# how to print with a reasonable number of significant figures:
pval_print <- signif(pval, 4)

beta <- unname(coef(summary(fit))[,'Estimate'][2])
# how to print with a reasonable number of significant figures:
beta_print <- signif(beta, 4)
```

@@

Whether standardization reflects an emergence of specialized production is associated with the number of producers, which distinguishes mechanical standardization from intentional standardization expressed by stylish and functional attributes [@Costin2001; @Costin1995]. In other words, mechanical standardization depends on potter's skills and experiences that increased morphological uniformity normally reflects fewer producers. The population could be an indicator to estimate potential number of producer. According to the historical records [@Nakamura1938, pp. 12], the population in Kiwulan reached higher number in the 17th century as the European presence and then decreased in the Chinese period due to a movement of indigenous people to the south [@Chen2007]. The decline in population is supported by ceramic abundance in total, which indicates less population might be a factor leading to higher standardization in the Chinese period.
